No need to know: astrophysics-free gravitational-wave cosmology

### 2024-08-20 src/tex/ms.tex
[showyourwork] overleaf sync

\section{Biases observed in parametric models}
\label{ap:parametric bias}
% \new{Figure~\ref{fig:parametric bias} shows recovered posteriors on \Ho{} as inferred from 50 mock catalogs using both the \bpl{} and \plp{} parametric models.
% We find that the \plp{} model recovers \Ho{} posteriors that are largely symmetric about the true value, whereas the \bpl{} model typically finds more support for larger \Ho{} values.
% We note that \citep{pierra_study_2023} report an underestimate of \Ho{} with a fit of their Broken Power Law model to a single dataset generated with \plp, but their prior bounds on the maximum mass parameter do not extend below the injected value of that parameter, which in turn does not allow for the possibility of an overestimated \Ho{}.}

@@

% \begin{figure}
%     \centering
%     \includegraphics[width=0.5\linewidth]{figures/bias.pdf}
%     \caption{Recovered posteriors on \Ho{} from spectral siren analyses on 50 mock catalogs with the \plp{} (green) and \bpl{} (pink) parametric models. The true, injected value is shown by a vertical black line.}
%     \label{fig:parametric bias}
%     \script{bias_numbers.py}
% \end{figure}

>>>>

\section{Biases observed in parametric models}
\label{ap:parametric bias}
Figure~\ref{fig:parametric bias} shows recovered posteriors on \Ho{} as inferred from 50 mock catalogs using both the \bpl{} and \plp{} parametric models.
We find that the \plp{} model recovers \Ho{} posteriors that are largely symmetric about the true value, whereas the \bpl{} model typically finds more support for larger \Ho{} values.
We note that \citep{pierra_study_2023} report an underestimate of \Ho{} with a fit of their Broken Power Law model to a single dataset generated with \plp, but their prior bounds on the maximum mass parameter do not extend below the injected value of that parameter, which in turn does not allow for the possibility of an overestimated \Ho{}.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{figures/bias.pdf}
    \caption{Recovered posteriors on \Ho{} from spectral siren analyses on 50 mock catalogs with the \plp{} (green) and \bpl{} (pink) parametric models. The true, injected value is shown by a vertical black line.}
    \label{fig:parametric bias}
    \script{bias_numbers.py}
\end{figure}
